---
title: "PRAD"
author: "Kornel Kiełczewski"
date: "13 April 2016"
output: html_document
---


```{r}
library(readr)
library(dplyr)
setwd('scripts/r')
source('data-utils.R')
prad <- read_delim('../../download/mrna-rsem-normalized-2015-11-01/gdac.broadinstitute.org_PRAD.Merge_rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.Level_3.2015110100.0.0/PRAD.rnaseqv2__illuminahiseq_rnaseqv2__unc_edu__Level_3__RSEM_genes_normalized__data.data.txt', delim = '\t')

raw.counts <- prad[-1,]
raw.counts$HybRefShort <- hyb.ref.short(raw.counts)

tumor.name <- 'PRAD'

data <- get.gene.table(raw.counts, tumor.name)$gene.table 
data$`Hybridization REF` <- NULL
r <- rownames(data)
data <- as.data.frame(sapply(data[,-1], as.numeric))
rownames(data) <- r
data <- as.data.frame(t(data))

subtypes.raw <- read.csv('../../data/Table_S1_PRAD.csv', sep = ';', stringsAsFactors = F)

data$PATIENT_ID <- sub('(\\w+-\\w+-\\w+).*', '\\1', rownames(data))

subtype.data <- data %>% inner_join(subtypes.raw, by = c('PATIENT_ID' = 'PATIENT_ID'))

a <- aov(subtype.data$ZNF195 ~ subtype.data$Subtype)
t.hsd <- TukeyHSD(a)
```



data$subtype <- sapply(rownames(data), function(rowname) {
  matching.indices <- sapply(subtypes.raw$SAMPLE_ID, function(s) grepl(s, rowname))
  if (length(which(matching.indices == T)) == 0) {
    NA
  } else {
    as.character(subtypes.raw[matching.indices,c('Subtype')])
  }
})


```{r}
# genes <- read.csv('../../data/KRAB ZNF gene master list.csv', sep = '\t')
# genes$Gene.ID <- as.character(genes$Gene.ID)
# 
# joined <- genes %>% inner_join(raw.counts, by = c('Gene.ID' = 'HybRefShort'))
# missing <- data.frame(Gene.ID = setdiff(genes$Gene.ID, rawdata$HybRefShort), tumor = tumor.name)
# joined$Ensembl.ID <- NULL  
# 
# rownames(joined) <- joined$Gene.ID
# joined$Gene.ID <- NULL
#colnames(joined) <- patient.code.to.type(colnames(joined))


subtypes.raw <- read.csv('../../data/Table_S1_PRAD.csv', sep = ';')

first.row <- filtered.counts[1,]

for (cc in 1:nrow(subtypes.raw)) {
  c <- subtypes.raw[cc,]$SAMPLE_ID
  s <- as.character(subtypes.raw[cc,]$Subtype)
  w <- which(grepl(c, colnames(first.row)) == T)
  if (length(w) != 0){
    print(s)
    colnames(first.row)[w] <- s
  }
}
colnames(first.row)

x <- first.row[,!grepl('TCGA', colnames(first.row))]

colnames(x) <- sub('\\..*', '', colnames(x))

x <- t(x)

for (c in unique(rownames(x))) {
  z <- x[rownames(x) == c]
  print(sprintf('%s: %s', toString(c), toString(z)))
  qqnorm(as.numeric(z))
}

ESG <- c(311.5345, 428.2857, 280.7298, 440.2036, 578.3722, 305.7823, 354.6479, 367.0954, 293.8747, 467.7501, 433.7126, 420.2765, 424.0401, 433.6328, 511.7574, 279.9685, 613.5820, 353.6156, 346.9157, 380.0635, 301.7751, 360.1066, 281.3469, 328.7106, 304.6062, 359.3305, 259.6416, 346.2810, 472.5111, 393.5549, 346.9773, 551.4833, 343.7981, 313.6852, 339.9259, 287.0407, 595.4845, 423.5650, 446.7393, 491.4034, 363.6708, 430.2885, 394.9822, 480.6950, 281.7431, 292.2780, 392.8049, 738.9306, 501.2686, 395.5990, 433.9623, 319.7821, 641.9805)

ETV <- c(416.6837, 552.9744, 546.9244, 494.7781, 309.3180, 384.4891, 334.7639, 356.8655, 453.9823, 358.1565, 393.3579)

FLI <- c(350.7069, 339.1792)

other <- c(371.5823, 283.5050, 321.2446, 361.6087, 328.6128, 411.5724, 399.5368, 346.2312, 271.5988, 342.9395, 252.8289, 348.9455, 392.9978, 227.6577, 394.5098, 349.3617, 370.0034, 386.1359, 261.9146, 291.9540, 506.6927, 254.6191, 270.5036, 359.9865, 454.5061)

ETV4 <- c(204.7244, 505.0195)
SPOP <- c(395.3571, 300.5498, 325.7185, 326.9079, 245.7786, 281.1780, 430.4668, 397.0917, 325.9164, 470.9302, 343.7599)
#FOXA1 <- c(280.2956)

groups <- c(rep('ESG', length(ESG)), rep('ETV', length(ETV)), rep('FLI', length(FLI)), rep('other', length(other)), 
            rep('ETV4', length(ETV4)), rep('SPOP', length(SPOP)))

all <- c(ESG, ETV, FLI, other, ETV4, SPOP)

bartlett.test(all, groups)


a <- aov(all ~ groups)
TukeyHSD(a)

```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
